### 2017-03-28 thesis/misc/appendix2.tex
tmp commit
finished editing up to the discussion

\begin{appendices}
	\crefalias{chapter}{appcha}
	\crefalias{section}{appsec}
	\renewcommand{\thesection}{\Alph{chapter}\arabic{section}}

@@

	\section{Comparison of the correlation of \gls{svd} and TM generated pathway metagenes}
	\label{sec:comparison_of_the_correlation_of_svd_and_tm_generated_pathway_metagenes}

@@

			\begin{tabular}{llr{\bfseries}S}

@@

	\begin{table}[htpb]
		\centering
		\caption[Description of the linear models constructed from the \gls{nzbc} data to predict the CrOl obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \acrshort{pr} pathway metagene score]{Description of the linear models constructed from the \gls{nzbc} data to predict the CrOl obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \gls{pr} pathway metagene score}
		\label{tab:lm_pr_only_crol}
		\begin{threeparttable}
			\begin{tabular}{llr{\bfseries}S}
				Linear Model & Variables & Estimate & {P-value}\\
					\hline
					\hline
					\rule{0pt}{2.25ex}\gls{pr} only                            & \gls{pr}   & 0.4484    & \bfseries \num{3.26d-06} \tnote{1} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & -0.002084 & 0.5699  \\
                                                                               & \gls{pr}   & 0.4497    & \bfseries \num{3.36d-06} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & -0.09307  & 0.1440   \\
                                                                               & Overweight & -0.01989  & 0.7750   \\
                                                                               & \gls{pr}   & 0.4418    & \bfseries \num{4.32d-06} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & 0.008072  & 0.2060   \\
                                                                               & Obese      & -0.2048   & 0.06100   \\
                                                                               & Overweight & -0.06159  & 0.4230   \\
                                                                               & \gls{pr}   & 0.4294    & \bfseries \num{7.93d-06} \\
					\hline
					\hline
			\end{tabular}
				\begin{tablenotes}
					\begin{footnotesize}
					\item [1] All values in bold are statistically significant (p \textless{} 0.05).
					\end{footnotesize}
				\end{tablenotes}
		\end{threeparttable}
	\end{table}

	\begin{table}[htpb]
		\centering
		\caption[Description of the linear models constructed from the \gls{nzbc} data to predict the Res obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \acrshort{pr} pathway metagene score]{Description of the linear models constructed from the \gls{nzbc} data to predict the Res obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \gls{pr} pathway metagene score}
		\label{tab:lm_pr_only_res}
		\begin{threeparttable}
			\begin{tabular}{llr \bfseries S}
				Linear Model & Variables & Estimate & {P-value}\\
					\hline
					\hline
					\rule{0pt}{2.25ex}\gls{pr} only                            & \gls{pr}   & 0.4926    & \bfseries \num{2.22d-07} \tnote{1}\\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & -0.001923 & 0.5904   \\
                                                                               & \gls{pr}   & 0.4938    & \bfseries \num{2.35d-07} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & -0.08315  & 0.1790   \\
                                                                               & Overweight & 0.0001257 & 0.9990   \\
                                                                               & \gls{pr}   & 0.4862    & \bfseries \num{3.00d-07} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & 0.007716  & 0.2140   \\
                                                                               & Obese      & -0.1899   & 0.0740   \\
                                                                               & Overweight & -0.03974  & 0.5950   \\
                                                                               & \gls{pr}   & 0.4744    & \bfseries \num{5.78d-07} \\
					\hline
					\hline
			\end{tabular}
				\begin{tablenotes}
					\begin{footnotesize}
					\item [1] All values in bold are statistically significant (p \textless{} 0.05).
					\end{footnotesize}
				\end{tablenotes}
		\end{threeparttable}
	\end{table}

	\begin{table}[htpb]
		\centering
		\caption[Description of the linear models constructed from the \gls{nzbc} data to predict the ResOl obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \acrshort{pr} pathway metagene score]{Description of the linear models constructed from the \gls{nzbc} data to predict the ResOl obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \gls{pr} pathway metagene score}
		\label{tab:lm_pr_only_resol}
		\begin{threeparttable}
			\begin{tabular}{llr{\bfseries}S}
				Linear Model & Variables & Estimate & {P-value}\\
					\hline
					\hline
					\rule{0pt}{2.25ex}\gls{pr} only                            & \gls{pr}   & 0.4581    & \bfseries \num{1.86d-06} \tnote{1}\\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & -0.001457 & 0.6897   \\
                                                                               & \gls{pr}   & 0.4590    & \bfseries \num{1.99d-06} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & -0.07789  & 0.2200   \\
                                                                               & Overweight & -0.01336  & 0.8480   \\
                                                                               & \gls{pr}   & 0.4526    & \bfseries \num{2.56d-06} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & 0.007763  & 0.2230   \\
                                                                               & Obese      & -0.1853   & 0.0890   \\
                                                                               & Overweight & -0.05346  & 0.4860   \\
                                                                               & \gls{pr}   & 0.4407    & \bfseries \num{4.71d-06} \\
					\hline
					\hline
			\end{tabular}
				\begin{tablenotes}
					\begin{footnotesize}
					\item [1] All values in bold are statistically significant (p \textless{} 0.05).
					\end{footnotesize}
				\end{tablenotes}
		\end{threeparttable}
	\end{table}

	\begin{table}[htpb]
		\centering
		\caption[Description of the linear models constructed from the \gls{nzbc} data to predict the Ca obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \acrshort{pr} pathway metagene score]{Description of the linear models constructed from the \gls{nzbc} data to predict the Ca obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \gls{pr} pathway metagene score}
		\label{tab:lm_pr_only_ca}
		\begin{threeparttable}
			\begin{tabular}{llr{\bfseries}S}
				Linear Model & Variables & Estimate & {P-value}\\
					\hline
					\hline
					\rule{0pt}{2.25ex}\gls{pr} only                            & \gls{pr}   & 0.3850    & \bfseries \num{8.34d-05} \tnote{1}\\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & -0.001538 & 0.6848    \\
                                                                               & \gls{pr}   & 0.3859    & \bfseries \num{8.67d-05}  \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & -0.07917  & 0.2274    \\
                                                                               & Overweight & 0.01954   & 0.7857    \\
                                                                               & \gls{pr}   & 0.3782    & \bfseries 0.0001060  \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & 0.008992  & 0.1718    \\
                                                                               & Obese      & -0.2036   & 0.07034   \\
                                                                               & Overweight & -0.02692  & 0.7338    \\
                                                                               & \gls{pr}   & 0.3644    & \bfseries 0.0001830  \\
					\hline
					\hline
			\end{tabular}
				\begin{tablenotes}
					\begin{footnotesize}
					\item [1] All values in bold are statistically significant (p \textless{} 0.05).
					\end{footnotesize}
				\end{tablenotes}
		\end{threeparttable}
	\end{table}

	\begin{table}[htpb]
		\centering
		\caption[Description of the linear models constructed from the \gls{nzbc} data to predict the CaOl obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \acrshort{pr} pathway metagene score]{Description of the linear models constructed from the \gls{nzbc} data to predict the CaOl obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \gls{pr} pathway metagene score}
		\label{tab:lm_pr_only_caol}
		\begin{threeparttable}
			\begin{tabular}{llr{\bfseries}S}
				Linear Model & Variables & Estimate & {P-value}\\
					\hline
					\hline
					\rule{0pt}{2.25ex}\gls{pr} only                            & \gls{pr}   & 0.3425     & \bfseries 0.0005200  \tnote{1}\\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & -0.0003869 & 0.9201    \\
                                                                               & \gls{pr}   & 0.3428     & \bfseries 0.0005530  \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & -0.05462   & 0.4147    \\
                                                                               & Overweight & 0.03092    & 0.6742    \\
                                                                               & \gls{pr}   & 0.3373     & \bfseries 0.0006470  \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & 0.008943   & 0.1842    \\
                                                                               & Obese      & -0.1784    & 0.1206    \\
                                                                               & Overweight & -0.01528   & 0.8504    \\
                                                                               & \gls{pr}   & 0.3236     & \bfseries 0.001060   \\
					\hline
					\hline
			\end{tabular}
				\begin{tablenotes}
					\begin{footnotesize}
					\item [1] All values in bold are statistically significant (p \textless{} 0.05).
					\end{footnotesize}
				\end{tablenotes}
		\end{threeparttable}
	\end{table}

	\begin{table}[htpb]
		\centering
		\caption[Description of the linear models constructed from the \gls{nzbc} data to predict the CaRes obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \acrshort{pr} pathway metagene score]{Description of the linear models constructed from the \gls{nzbc} data to predict the CaRes obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \gls{pr} pathway metagene score}
		\label{tab:lm_pr_only_cares}
		\begin{threeparttable}
			\begin{tabular}{llr{\bfseries}S}
				Linear Model & Variables & Estimate & {P-value}\\
					\hline
					\hline
					\rule{0pt}{2.25ex}\gls{pr} only                            & \gls{pr}   & -0.4255   & \bfseries \num{1.13d-05} \tnote{1}\\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & 0.001874  & 0.6140   \\
                                                                               & \gls{pr}   & -0.4267   & \bfseries \num{1.17d-05} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & 0.08159   & 0.2040   \\
                                                                               & Overweight & -0.02006  & 0.7760   \\
                                                                               & \gls{pr}   & -0.4186   & \bfseries \num{1.44d-05} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & -0.008379 & 0.1936   \\
                                                                               & Obese      & 0.1976    & 0.07310  \\
                                                                               & Overweight & 0.02323   & 0.7645   \\
                                                                               & \gls{pr}   & -0.4057   & \bfseries \num{2.59d-05} \\
					\hline
					\hline
			\end{tabular}
				\begin{tablenotes}
					\begin{footnotesize}
					\item [1] All values in bold are statistically significant (p \textless{} 0.05).
					\end{footnotesize}
				\end{tablenotes}
		\end{threeparttable}
	\end{table}

	\begin{table}[htpb]
		\centering
		\caption[Description of the linear models constructed from the \gls{nzbc} data to predict the CaResOl obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \acrshort{pr} pathway metagene score]{Description of the linear models constructed from the \gls{nzbc} data to predict the CaResOl obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \gls{pr} pathway metagene score}
		\label{tab:lm_pr_only_caresol}
		\begin{threeparttable}
			\begin{tabular}{llr{\bfseries}S}
				Linear Model & Variables & Estimate & {P-value}\\
					\hline
					\hline
					\rule{0pt}{2.25ex}\gls{pr} only                            & \gls{pr}   & 0.4094     & \bfseries \num{2.58d-05} \tnote{1}\\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & -1.809d-06 & 0.9996   \\
                                                                               & \gls{pr}   & 4.094d-01  & \bfseries \num{2.85d-05} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & -0.05775   & 0.3740   \\
                                                                               & Overweight & 0.02613    & 0.7140   \\
                                                                               & \gls{pr}   & 0.4041     & \bfseries \num{3.36d-05} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & 0.01045    & 0.1091   \\
                                                                               & Obese      & -0.2024    & 0.06910  \\
                                                                               & Overweight & -0.02786   & 0.7220   \\
                                                                               & \gls{pr}   & 0.3881     & \bfseries \num{6.21d-05} \\
					\hline
					\hline
			\end{tabular}
				\begin{tablenotes}
					\begin{footnotesize}
					\item [1] All values in bold are statistically significant (p \textless{} 0.05).
					\end{footnotesize}
				\end{tablenotes}
		\end{threeparttable}
	\end{table}

	\begin{table}[htpb]
		\centering
		\caption[Description of the linear models constructed from the \gls{nzbc} data to predict the Or obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \acrshort{pr} pathway metagene score]{Description of the linear models constructed from the \gls{nzbc} data to predict the Or obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \gls{pr} pathway metagene score}
		\label{tab:lm_pr_only_or}
		\begin{threeparttable}
			\begin{tabular}{llr{\bfseries}S}
				Linear Model & Variables & Estimate & {P-value}\\
					\hline
					\hline
					\rule{0pt}{2.25ex}\gls{pr} only                            & \gls{pr}   & -0.4463   & \bfseries \num{3.66d-06} \tnote{1}\\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & 0.002108  & 0.5660   \\
                                                                               & \gls{pr}   & -0.4476   & \bfseries \num{3.77d-06} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & 0.088520  & 0.1650   \\
                                                                               & Overweight & 0.004028  & 0.9540   \\
                                                                               & \gls{pr}   & -0.4396   & \bfseries \num{4.82d-06} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & -0.007866 & 0.2180   \\
                                                                               & Obese      & 0.1974    & 0.07100  \\
                                                                               & Overweight & 0.04466   & 0.5620   \\
                                                                               & \gls{pr}   & -0.4275   & \bfseries \num{8.77d-06} \\
					\hline
					\hline
			\end{tabular}
				\begin{tablenotes}
					\begin{footnotesize}
					\item [1] All values in bold are statistically significant (p \textless{} 0.05).
					\end{footnotesize}
				\end{tablenotes}
		\end{threeparttable}
	\end{table}

>>>>

% \begin{appendices}
% 	\crefalias{chapter}{appcha}
% 	\crefalias{section}{appsec}
% 	\renewcommand{\thesection}{\Alph{chapter}\arabic{section}}

@@

	\section{Visual comparison of the correlation of \gls{svd} and TM generated pathway metagenes}
	\label{sec:comparison_of_the_correlation_of_svd_and_tm_generated_pathway_metagenes}

@@

			\begin{tabular}{llrc}

@@

	\begin{table}[htpb]
		\centering
		\caption[Description of the linear models constructed from the \gls{nzbc} data to predict the CrOl obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \acrshort{pr} pathway metagene score]{Description of the linear models constructed from the \gls{nzbc} data to predict the CrOl obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \gls{pr} pathway metagene score}
		\label{tab:lm_pr_only_crol}
		\begin{threeparttable}
			\begin{tabular}{llrc}
				Linear Model & Variables & Estimate & {P-value}\\
					\hline
					\hline
					\rule{0pt}{2.25ex}\gls{pr} only                            & \gls{pr}   & 0.4484    & \bfseries \num{3.26d-06} \tnote{1} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & -0.002084 & 0.5699  \\
                                                                               & \gls{pr}   & 0.4497    & \bfseries \num{3.36d-06} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & -0.09307  & 0.1440   \\
                                                                               & Overweight & -0.01989  & 0.7750   \\
                                                                               & \gls{pr}   & 0.4418    & \bfseries \num{4.32d-06} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & 0.008072  & 0.2060   \\
                                                                               & Obese      & -0.2048   & 0.06100   \\
                                                                               & Overweight & -0.06159  & 0.4230   \\
                                                                               & \gls{pr}   & 0.4294    & \bfseries \num{7.93d-06} \\
					\hline
					\hline
			\end{tabular}
				\begin{tablenotes}
					\begin{footnotesize}
					\item [1] All values in bold are statistically significant (p \textless{} 0.05).
					\end{footnotesize}
				\end{tablenotes}
		\end{threeparttable}
	\end{table}

	\begin{table}[htpb]
		\centering
		\caption[Description of the linear models constructed from the \gls{nzbc} data to predict the Res obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \acrshort{pr} pathway metagene score]{Description of the linear models constructed from the \gls{nzbc} data to predict the Res obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \gls{pr} pathway metagene score}
		\label{tab:lm_pr_only_res}
		\begin{threeparttable}
			\begin{tabular}{llrc}
				Linear Model & Variables & Estimate & {P-value}\\
					\hline
					\hline
					\rule{0pt}{2.25ex}\gls{pr} only                            & \gls{pr}   & 0.4926    & \bfseries \num{2.22d-07} \tnote{1}\\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & -0.001923 & 0.5904   \\
                                                                               & \gls{pr}   & 0.4938    & \bfseries \num{2.35d-07} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & -0.08315  & 0.1790   \\
                                                                               & Overweight & 0.0001257 & 0.9990   \\
                                                                               & \gls{pr}   & 0.4862    & \bfseries \num{3.00d-07} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & 0.007716  & 0.2140   \\
                                                                               & Obese      & -0.1899   & 0.0740   \\
                                                                               & Overweight & -0.03974  & 0.5950   \\
                                                                               & \gls{pr}   & 0.4744    & \bfseries \num{5.78d-07} \\
					\hline
					\hline
			\end{tabular}
				\begin{tablenotes}
					\begin{footnotesize}
					\item [1] All values in bold are statistically significant (p \textless{} 0.05).
					\end{footnotesize}
				\end{tablenotes}
		\end{threeparttable}
	\end{table}

	\begin{table}[htpb]
		\centering
		\caption[Description of the linear models constructed from the \gls{nzbc} data to predict the ResOl obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \acrshort{pr} pathway metagene score]{Description of the linear models constructed from the \gls{nzbc} data to predict the ResOl obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \gls{pr} pathway metagene score}
		\label{tab:lm_pr_only_resol}
		\begin{threeparttable}
			\begin{tabular}{llrc}
				Linear Model & Variables & Estimate & {P-value}\\
					\hline
					\hline
					\rule{0pt}{2.25ex}\gls{pr} only                            & \gls{pr}   & 0.4581    & \bfseries \num{1.86d-06} \tnote{1}\\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & -0.001457 & 0.6897   \\
                                                                               & \gls{pr}   & 0.4590    & \bfseries \num{1.99d-06} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & -0.07789  & 0.2200   \\
                                                                               & Overweight & -0.01336  & 0.8480   \\
                                                                               & \gls{pr}   & 0.4526    & \bfseries \num{2.56d-06} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & 0.007763  & 0.2230   \\
                                                                               & Obese      & -0.1853   & 0.0890   \\
                                                                               & Overweight & -0.05346  & 0.4860   \\
                                                                               & \gls{pr}   & 0.4407    & \bfseries \num{4.71d-06} \\
					\hline
					\hline
			\end{tabular}
				\begin{tablenotes}
					\begin{footnotesize}
					\item [1] All values in bold are statistically significant (p \textless{} 0.05).
					\end{footnotesize}
				\end{tablenotes}
		\end{threeparttable}
	\end{table}

	\begin{table}[htpb]
		\centering
		\caption[Description of the linear models constructed from the \gls{nzbc} data to predict the Ca obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \acrshort{pr} pathway metagene score]{Description of the linear models constructed from the \gls{nzbc} data to predict the Ca obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \gls{pr} pathway metagene score}
		\label{tab:lm_pr_only_ca}
		\begin{threeparttable}
			\begin{tabular}{llrc}
				Linear Model & Variables & Estimate & {P-value}\\
					\hline
					\hline
					\rule{0pt}{2.25ex}\gls{pr} only                            & \gls{pr}   & 0.3850    & \bfseries \num{8.34d-05} \tnote{1}\\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & -0.001538 & 0.6848    \\
                                                                               & \gls{pr}   & 0.3859    & \bfseries \num{8.67d-05}  \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & -0.07917  & 0.2274    \\
                                                                               & Overweight & 0.01954   & 0.7857    \\
                                                                               & \gls{pr}   & 0.3782    & \bfseries 0.0001060  \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & 0.008992  & 0.1718    \\
                                                                               & Obese      & -0.2036   & 0.07034   \\
                                                                               & Overweight & -0.02692  & 0.7338    \\
                                                                               & \gls{pr}   & 0.3644    & \bfseries 0.0001830  \\
					\hline
					\hline
			\end{tabular}
				\begin{tablenotes}
					\begin{footnotesize}
					\item [1] All values in bold are statistically significant (p \textless{} 0.05).
					\end{footnotesize}
				\end{tablenotes}
		\end{threeparttable}
	\end{table}

	\begin{table}[htpb]
		\centering
		\caption[Description of the linear models constructed from the \gls{nzbc} data to predict the CaOl obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \acrshort{pr} pathway metagene score]{Description of the linear models constructed from the \gls{nzbc} data to predict the CaOl obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \gls{pr} pathway metagene score}
		\label{tab:lm_pr_only_caol}
		\begin{threeparttable}
			\begin{tabular}{llrc}
				Linear Model & Variables & Estimate & {P-value}\\
					\hline
					\hline
					\rule{0pt}{2.25ex}\gls{pr} only                            & \gls{pr}   & 0.3425     & \bfseries 0.0005200  \tnote{1}\\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & -0.0003869 & 0.9201    \\
                                                                               & \gls{pr}   & 0.3428     & \bfseries 0.0005530  \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & -0.05462   & 0.4147    \\
                                                                               & Overweight & 0.03092    & 0.6742    \\
                                                                               & \gls{pr}   & 0.3373     & \bfseries 0.0006470  \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & 0.008943   & 0.1842    \\
                                                                               & Obese      & -0.1784    & 0.1206    \\
                                                                               & Overweight & -0.01528   & 0.8504    \\
                                                                               & \gls{pr}   & 0.3236     & \bfseries 0.001060   \\
					\hline
					\hline
			\end{tabular}
				\begin{tablenotes}
					\begin{footnotesize}
					\item [1] All values in bold are statistically significant (p \textless{} 0.05).
					\end{footnotesize}
				\end{tablenotes}
		\end{threeparttable}
	\end{table}

	\begin{table}[htpb]
		\centering
		\caption[Description of the linear models constructed from the \gls{nzbc} data to predict the CaRes obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \acrshort{pr} pathway metagene score]{Description of the linear models constructed from the \gls{nzbc} data to predict the CaRes obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \gls{pr} pathway metagene score}
		\label{tab:lm_pr_only_cares}
		\begin{threeparttable}
			\begin{tabular}{llrc}
				Linear Model & Variables & Estimate & {P-value}\\
					\hline
					\hline
					\rule{0pt}{2.25ex}\gls{pr} only                            & \gls{pr}   & -0.4255   & \bfseries \num{1.13d-05} \tnote{1}\\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & 0.001874  & 0.6140   \\
                                                                               & \gls{pr}   & -0.4267   & \bfseries \num{1.17d-05} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & 0.08159   & 0.2040   \\
                                                                               & Overweight & -0.02006  & 0.7760   \\
                                                                               & \gls{pr}   & -0.4186   & \bfseries \num{1.44d-05} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & -0.008379 & 0.1936   \\
                                                                               & Obese      & 0.1976    & 0.07310  \\
                                                                               & Overweight & 0.02323   & 0.7645   \\
                                                                               & \gls{pr}   & -0.4057   & \bfseries \num{2.59d-05} \\
					\hline
					\hline
			\end{tabular}
				\begin{tablenotes}
					\begin{footnotesize}
					\item [1] All values in bold are statistically significant (p \textless{} 0.05).
					\end{footnotesize}
				\end{tablenotes}
		\end{threeparttable}
	\end{table}

	\begin{table}[htpb]
		\centering
		\caption[Description of the linear models constructed from the \gls{nzbc} data to predict the CaResOl obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \acrshort{pr} pathway metagene score]{Description of the linear models constructed from the \gls{nzbc} data to predict the CaResOl obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \gls{pr} pathway metagene score}
		\label{tab:lm_pr_only_caresol}
		\begin{threeparttable}
			\begin{tabular}{llrc}
				Linear Model & Variables & Estimate & {P-value}\\
					\hline
					\hline
					\rule{0pt}{2.25ex}\gls{pr} only                            & \gls{pr}   & 0.4094     & \bfseries \num{2.58d-05} \tnote{1}\\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & -1.809d-06 & 0.9996   \\
                                                                               & \gls{pr}   & 4.094d-01  & \bfseries \num{2.85d-05} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & -0.05775   & 0.3740   \\
                                                                               & Overweight & 0.02613    & 0.7140   \\
                                                                               & \gls{pr}   & 0.4041     & \bfseries \num{3.36d-05} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & 0.01045    & 0.1091   \\
                                                                               & Obese      & -0.2024    & 0.06910  \\
                                                                               & Overweight & -0.02786   & 0.7220   \\
                                                                               & \gls{pr}   & 0.3881     & \bfseries \num{6.21d-05} \\
					\hline
					\hline
			\end{tabular}
				\begin{tablenotes}
					\begin{footnotesize}
					\item [1] All values in bold are statistically significant (p \textless{} 0.05).
					\end{footnotesize}
				\end{tablenotes}
		\end{threeparttable}
	\end{table}

	\begin{table}[htpb]
		\centering
		\caption[Description of the linear models constructed from the \gls{nzbc} data to predict the Or obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \acrshort{pr} pathway metagene score]{Description of the linear models constructed from the \gls{nzbc} data to predict the Or obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \gls{pr} pathway metagene score}
		\label{tab:lm_pr_only_or}
		\begin{threeparttable}
			\begin{tabular}{llrc}
				Linear Model & Variables & Estimate & {P-value}\\
					\hline
					\hline
					\rule{0pt}{2.25ex}\gls{pr} only                            & \gls{pr}   & -0.4463   & \bfseries \num{3.66d-06} \tnote{1}\\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & 0.002108  & 0.5660   \\
                                                                               & \gls{pr}   & -0.4476   & \bfseries \num{3.77d-06} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & 0.088520  & 0.1650   \\
                                                                               & Overweight & 0.004028  & 0.9540   \\
                                                                               & \gls{pr}   & -0.4396   & \bfseries \num{4.82d-06} \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & -0.007866 & 0.2180   \\
                                                                               & Obese      & 0.1974    & 0.07100  \\
                                                                               & Overweight & 0.04466   & 0.5620   \\
                                                                               & \gls{pr}   & -0.4275   & \bfseries \num{8.77d-06} \\
					\hline
					\hline
			\end{tabular}
				\begin{tablenotes}
					\begin{footnotesize}
					\item [1] All values in bold are statistically significant (p \textless{} 0.05).
					\end{footnotesize}
				\end{tablenotes}
		\end{threeparttable}
	\end{table}

	\begin{table}[htpb]
		\centering
		\caption[Description of the linear models constructed from the \gls{nzbc} data to predict the FM obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \acrshort{pr} pathway metagene score]{Description of the linear models constructed from the \gls{nzbc} data to predict the FM obesity, using only the sample \gls{bmi}, \gls{bmi} status and the \gls{pr} pathway metagene score}
		\label{tab:lm_pr_only_fm}
		\begin{threeparttable}
			\begin{tabular}{llrc}
				Linear Model & Variables & Estimate & {P-value}\\
					\hline
					\hline
					\rule{0pt}{2.25ex}\gls{pr} only                            & \gls{pr}   & -0.1285  & 0.2050   \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & 0.002446 & 0.5479   \\
                                                                               & \gls{pr}   & -0.1301  & 0.2012   \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & -0.08819 & 0.2080   \\
                                                                               & Overweight & -0.1488  & 0.05500  \\
                                                                               & \gls{pr}   & -0.1306  & 0.1940   \\
					\hline
					\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & 0.01619  & \bfseries 0.02008 \tnote{1}\\
                                                                               & Obese      & -0.3123  & \bfseries 0.008750  \\
                                                                               & Overweight & -0.2324  & \bfseries 0.006030  \\
                                                                               & \gls{pr}   & -0.1554  & 0.1165   \\
					\hline
					\hline
			\end{tabular}
				\begin{tablenotes}
					\begin{footnotesize}
					\item [1] All values in bold are statistically significant (p \textless{} 0.05).
					\end{footnotesize}
				\end{tablenotes}
		\end{threeparttable}
	\end{table}
